# Parts

You can add parts to organize one or more book chapters together. Parts can be inserted at the top of an .Rmd file, before the first-level chapter heading in that same file. 

Add a numbered part: `# (PART) Act one {-}` (followed by `# A chapter`)

Add an unnumbered part: `# (PART\*) Act one {-}` (followed by `# A chapter`)

Add an appendix as a special kind of un-numbered part: `# (APPENDIX) Other stuff {-}` (followed by `# A chapter`). Chapters in an appendix are prepended with letters instead of numbers.

```{r hw-additive, echo=TRUE, fig.cap="Holt-Winters Aditivo: Últimos 7 días y pronóstico"}

hw_additive <- HoltWinters(ts_ventas, seasonal = "additive")
hw_additive_forecast <- forecast(hw_additive, h = 7)

p_hw_add <- autoplot(hw_additive_forecast) +
  labs(title = "Holt-Winters Aditivo: Ventas diarias",
       x = "Fecha", y = "Valor total") +
  theme_minimal()
p_hw_add

```

```{r hw-multiplicative, echo=TRUE, fig.cap="Holt-Winters Multiplicativo: Ventas diarias"}


hw_multiplicative <- HoltWinters(ts_ventas, seasonal = "multiplicative")
hw_multiplicative_forecast <- forecast(hw_multiplicative, h = 7)

p_hw_mult <- autoplot(hw_multiplicative_forecast) +
  labs(title = "Holt-Winters Multiplicativo: Ventas diarias",
       x = "Fecha", y = "Valor total") +
  theme_minimal()
p_hw_mult
```

```{r hw-compare, echo=TRUE}


# Precisión del modelo aditivo
accuracy_add <- accuracy(hw_additive_forecast)
# Precisión del modelo multiplicativo
accuracy_mult <- accuracy(hw_multiplicative_forecast)

# Mostrar RMSE y MAE
rbind(
  Additive = c(RMSE = accuracy_add[1, "RMSE"], MAE = accuracy_add[1, "MAE"]),
  Multiplicative = c(RMSE = accuracy_mult[1, "RMSE"], MAE = accuracy_mult[1, "MAE"])
)
```

```{r ses-log, echo=TRUE, fig.cap="Suavizamiento Exponencial Simple (log(y))"}


ses_log <- ses(ts_ventas_log, h = 7)

p_ses_log <- autoplot(ses_log) +
  labs(title = "Suavizamiento Exponencial Simple (log(y))",
       x = "Fecha", y = "Log(Valor total)") +
  theme_minimal()
p_ses_log
```

